The \dealii Library, Version 9.6

### 2024-07-10 9.6/paper.tex
Minor work on the tutorial/code gallery section.

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-87} was contributed by Magdalena Schreter-Fleischhacker
    (Technical University of Munich) and Peter Munch
    (University of Augsburg/Uppsala University). It
    presents the advanced point-evaluation functionalities of \dealii,
    specifically useful for evaluating finite element solutions at
    arbitrary points on finite element meshes that can be distributed among processes.
  \item
    \texttt{step-89} was contributed by Johannes Heinz (TU Wien),
    Maximilian Bergbauer (Technical University of Munich),
    Marco Feder (SISSA), and Peter Munch (University of Augsburg/Uppsala University).
    It shows one way how to apply non-matching and/or Chimera methods
    within matrix-free loops in \dealii.
  \item
    \texttt{step-90} was contributed by Vladimir Yushutin and Timo Heister (Clemson University).
    It implements the trace finite element method (TraceFEM). TraceFEM solves PDEs
    posed on a possibly evolving $(dim-1)$-dimensional surface $\Gamma$ employing
    a fixed uniform background mesh of a $dim$-dimensional domain in which
    the surface is embedded. Such surface PDEs arise in problems involving
    material films with complex properties and in other situations in which
    a non-trivial condition is imposed on either a stationary or a moving interface.
    Here we consider a steady, complex, non-trivial surface and the prototypical
    Laplace-Beltrami equation which is a counterpart of
    the Poisson problem on flat domains.
\end{itemize}

>>>>

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-83} if we can get it ready TODO  
  \item
    \texttt{step-86} if we can get it merged TODO  
  \item
    \texttt{step-87} was contributed by Magdalena Schreter-Fleischhacker
    (Technical University of Munich) and Peter Munch
    (University of Augsburg/Uppsala University). It
    presents the advanced point-evaluation functionalities of \dealii
    that are useful for evaluating finite element solutions at
    arbitrary points on finite element meshes that can be distributed among processes.
  \item
    \texttt{step-89} was contributed by Johannes Heinz (TU Wien),
    Maximilian Bergbauer (Technical University of Munich),
    Marco Feder (SISSA), and Peter Munch (University of Augsburg/Uppsala University).
    It shows one way how to apply non-matching and/or Chimera methods
    within matrix-free loops in \dealii.
  \item
    \texttt{step-90} was contributed by Vladimir Yushutin and Timo Heister (Clemson University).
    It implements the trace finite element method (TraceFEM). TraceFEM solves PDEs
    posed on a, possibly evolving, $(dim-1)$-dimensional surface $\Gamma$ employing
    a fixed uniform background mesh of a $dim$-dimensional domain in which
    the surface is embedded. Such surface PDEs arise in problems involving
    material films with complex properties and in other situations in which
    a non-trivial condition is imposed on either a stationary or a moving interface.
    The program considers a steady, complex, non-trivial surface and the prototypical
    Laplace-Beltrami equation which is a counterpart of
    the Poisson problem on flat domains.
\end{itemize}

In addition, there are three new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
UPDATE
\begin{itemize}
  \item \textit{``Crystal growth phase field model'''},
    contributed by Umair Hussain;
  \item \textit{``Nonlinear heat transfer problem''}, contributed by
    Narasimhan Swaminathan;
  \item \textit{``Traveling-wave solutions of a qualitative model for combustion waves''}, contributed by
    Shamil Magomedov.
\end{itemize}
